### 2017-05-04 02-background.tex
Start working on integration: block out double algorithm, unify symbol usage

\section{Background}
% In this section, we briefly review the Bayesian model we are considering in this paper.

@@

\begin{algorithm}[t]
\caption{Sequential version of SG-MCMC for a-MMSB}\label{alg}
\begin{algorithmic}[1]
\STATE Initialize $\pi , \bt, \phi, \ta$
\WHILE {sampling}
\STATE Sample mini-batch of vertex pairs \Minibatch from \Edges or $E$
\FOR {each vertex in \Minibatch}
    \STATE Sample mini-batch of vertices $\Neighbors$ from $\Vertices$
    \STATE Update $\phi_{a}$ using Eq.~\ref{eqn:local_update}
  %  $\phi_{a}^* \law \left| \phi_{a} + \f{\ep_{\phi}}{2} \left( \al - \phi_{a} + \f{N}{|\Neighbors|} \sum_{b \in \Neighbors} G_{\phi_{a}}\right) + (\phi_{a})^{\ha} \xi_{a}\right|$
    \STATE Obtain $\pi_a$ from $\phi_a^*$ \ENDFOR
\FOR {$k = 1,\dots,K$}
    \STATE Update $\ta_{k}$ using Eq.~\ref{eqn:global_update}
   % $\ta_{k}^* \law \left| \ta_{k} + \f{\ep_\ta}{2} \left( \eta - \ta_{k} + h(\cE_t) \sum_{(a,b) \in \cE_t} G_{\ta_{k}}(a,b) \right) + (\ta_{k})^{\ha}\xi_{k} \right|$
    \STATE Obtain $\bt_k$ from $\ta_k^*$
\ENDFOR
\ENDWHILE
\end{algorithmic}
\label{algorithm}
\end{algorithm}

\addtolength{\tabcolsep}{-3pt}
\renewcommand{\arraystretch}{1.5}
\begin{table}[b] % [htbp]
\center
\begin{tabular}{c C{0.075\textwidth} c L{0.26\textwidth}}
\textbf{symbol}
	 & \textbf{type} & \textbf{size} & \textbf{description} \\
         % & \multicolumn{1}{c}{\textbf{type}}
                           % & \multicolumn{1}{c}{\textbf{description}} \\
\hline
$\cK$      &              & $K$        & set of communities \\
\Vertices  & \{vertex\}   & $N$          & vertices in the graph \\
\Edges     & \{edge\}     &              & linked edges in the graph \\
$E$        & \{edge\}     &              & $\Vertices\times\Vertices$: linked and nonlinked edges \\
\Heldout   & \{edge\}     &              & held-out subset of the graph \\
\Minibatch & \{edge\}     &              & sampled mini-batch of edges in~$E$ \\
$M$        &              &              & number of vertices in \Minibatch \\
\Neighbors & \{vertex\}   &              & sampled neighbor set for a vertex in~\Minibatch \\
$\theta$   & float~vector 2-D & $K\times{}2$ & reparameterization of $\beta$.
					$\beta[k] = \theta[k][1] / \sum_j\theta[k][j]$ \\
$\beta$    & float vector & $K$          & community strength \\
$\phi$     & float~vector 2-D & $N\times{}K$ & reparameterization of $\pi$.
					$\pi[i][k] = \phi[i][k] / \sum_j\phi[i][j]$ \\
$\pi$      & float~vector 2-D & $N\times{}K$ &
					$\pi[i][k]$~is~probability that vertex $i$ is in community $k$ \\
\hline
\end{tabular}
\caption{Definition of most important symbols}
\label{tbl-symbols}
\end{table}
\addtolength{\tabcolsep}{3pt}
\renewcommand{\arraystretch}{1.0}

@@

\subsection{Related work on parallel community detection}

Among previous work on parallelizing MMSB algorithms, we mention the Online
Tensor approach~\cite{DBLP:journals/corr/HuangNHVA13} on GPUs, and our previous
parallel implementation of SG-MCMC on GPUs and multi-core CPUs (submitted for
publication). There are a few projects that did a distributed implementation
for community detection on very large network graphs. In contrast to our work,
they all detect non-overlapping communities: \cite{Bu2013246} investigate a
large number of networks; \cite{2015arXiv150302115L} investigate hierarchical
stochastic blockmodels; \cite{Prat-Perez:2014:HQS:2566486.2568010} use
multi-core machines.

\begin{comment}
In this paper, we describe our custom RDMA D-KV (Distributed Key-Value)
store. Current RMDA D-KV store implementations are RamCloud~\cite{RamCloud},
Pilaf~\cite{Pilaf}, Herd~\cite{Herd} and FaRM~\cite{FaRM}. All these systems
use RDMA to implement a D-KV store. However, all of them are far more powerful
than our custom implementation -- and this power comes at a cost that we
can avoid. They implement a generic D-KV store that controls concurrency,
supports dynamic inserts and deletes, supports variable-sized values
(whose size may change at an update), and keys of arbitrary type. Because
of the nature of our distributed algorithm, we have to deal with none of
these issues. For us, values are fixed-size, allocated only at the initial
population, and remain alive forever. We have no concurrency between writes
and reads or other writes. Our keys are a contiguous range of integers. All
these properties together allow an extremely low-overhead implementation
that does not involve the remote host in any transaction.
\end{comment}

>>>>

\section{Background}
\label{sec-background}
% In this section, we briefly review the Bayesian model we are considering in this paper.

@@

\begin{algorithm}[t]
\caption{Sequential version of SG-MCMC for a-MMSB}\label{alg}
\begin{algorithmic}[1]
\STATE Initialize $\pi , \bt, \phi, \ta$
\WHILE {sampling}
\STATE Sample mini-batch of vertex pairs \Minibatch from \Edges or $E$
\FOR {each vertex in \Minibatch}
    \STATE Sample mini-batch of vertices $\Neighbors$ from $\Vertices$
    \STATE \texttt{update\_phi:} Update $\phi_{a}$ using Eq.~\ref{eqn:local_update} \ENDFOR
  %  $\phi_{a}^* \law \left| \phi_{a} + \f{\ep_{\phi}}{2} \left( \al - \phi_{a} + \f{N}{|\Neighbors|} \sum_{b \in \Neighbors} G_{\phi_{a}}\right) + (\phi_{a})^{\ha} \xi_{a}\right|$
\FOR {each vertex in \Minibatch}
    \STATE \texttt{update\_pi:} Obtain $\pi_a$ from $\phi_a^*$ \ENDFOR
\FOR {$k = 1,\dots,K$}
    \STATE \texttt{update\_theta:} Update $\ta_{k}$ using Eq.~\ref{eqn:global_update} \ENDFOR
\FOR {$k = 1,\dots,K$}
   % $\ta_{k}^* \law \left| \ta_{k} + \f{\ep_\ta}{2} \left( \eta - \ta_{k} + h(\cE_t) \sum_{(a,b) \in \cE_t} G_{\ta_{k}}(a,b) \right) + (\ta_{k})^{\ha}\xi_{k} \right|$
    \STATE \texttt{update\_beta:} Obtain $\bt_k$ from $\ta_k^*$ \ENDFOR
\ENDWHILE
\end{algorithmic}
\label{algorithm}
\end{algorithm}

\addtolength{\tabcolsep}{-3pt}
\renewcommand{\arraystretch}{1.5}
\begin{table}[b] % [htbp]
\center
\begin{tabular}{c C{0.075\textwidth} c L{0.26\textwidth}}
\textbf{symbol}
	 & \textbf{type} & \textbf{size} & \textbf{description} \\
         % & \multicolumn{1}{c}{\textbf{type}}
                           % & \multicolumn{1}{c}{\textbf{description}} \\
\hline
$\cK$      &              & $K$        & set of communities \\
\Vertices  & \{vertex\}   & $N$          & vertices in the graph \\
\Edges     & \{edge\}     &              & linked edges in the graph \\
$E$        & \{edge\}     &              & $\Vertices\times\Vertices$: linked and nonlinked edges \\
\Heldout   & \{edge\}     &              & held-out subset of the graph \\
\Minibatch & \{edge\}     &              & sampled mini-batch of edges in~$E$ \\
$M$        &              &              & number of vertices in \Minibatch \\
\Neighbors & \{vertex\}   &              & sampled neighbor set for a vertex in~\Minibatch \\
$\theta$   & float~vector 2-D & $K\times{}2$ & reparameterization of $\beta$.
					$\beta[k] = \theta[k][1] / \sum_j\theta[k][j]$ \\
$\beta$    & float vector & $K$          & community strength \\
$\phi$     & float~vector 2-D & $N\times{}K$ & reparameterization of $\pi$.
					$\pi[i][k] = \phi[i][k] / \sum_j\phi[i][j]$ \\
$\pi$      & float~vector 2-D & $N\times{}K$ &
					$\pi[i][k]$~is~probability that vertex $i$ is in community $k$ \\
\hline
\\[-3ex]
\end{tabular}
\caption{Definition of most important symbols}
\label{tbl-symbols}
\end{table}
\addtolength{\tabcolsep}{3pt}
\renewcommand{\arraystretch}{1.0}

@@
